---
title: "My First Episode"
teaching: 15
exercises: 30
---

:::::::::::::::::::::::::::::::::::::: questions 

- How do you write a new episode using RMarkdown and `{sandpaper}`?

::::::::::::::::::::::::::::::::::::::::::::::::

::::::::::::::::::::::::::::::::::::: objectives

- Explain how to use markdown to modify the episode in the new lesson template
- Demonstrate how to include pieces of code, figures, and nested challenge blocks

::::::::::::::::::::::::::::::::::::::::::::::::

## Introduction

This is the new Carpentries template. It is written in [RMarkdown][r-markdown],
which is a variant of Markdown that allows you to render code inside the
lesson. Please refer to the [lesson
example](https://carpentries.github.io/lesson-example) for full documentation.

What you need to know is that there are three block quotes required for a valid
Carpentries lesson template:

 1. `questions` are displayed at the beginning of the episode to prime the
    learner for the content.
 2. `objectives` are the learning objectives for an episode displayed with
    the questions.
 3. `keypoints` are displayed at the end of the episode to reinforce the
    objectives.

At this point, we have updated the title, questions and objectives. Next we will look at adding a challenge block using fenced-divs (the series of colons, minimally 3).

::: Caution
This is a callout block but with only 3 colons for the fenced-div, it may be overlooked. Avoid this potential pitfall by including more than 3 colons to make the lines stand out easily. Notice that the rest of this .Rmd file follows this advice.
:::

::::::::::::::::::::::::::::::::::::: challenge 

## Challenge 1: Can you print your R session information?

What is the output of this command?

```{r, eval = FALSE}
sessionInfo()
```

:::::::::::::::::::::::: solution 

## Output
 
```{r, echo = FALSE}
cat("R version 4.0.3 (2020-10-10)",
"Platform: x86_64-apple-darwin17.0 (64-bit)",
"Running under: macOS Mojave 10.14.6", sep = "\n")
```

*Note that your session may look different than the output below depending on your individual computer setup.
:::::::::::::::::::::::::::::::::


## Challenge 2: how do you nest solutions within challenge blocks?

:::::::::::::::::::::::: solution 

You can add a line with at least three colons and a `solution` tag.

:::::::::::::::::::::::::::::::::
::::::::::::::::::::::::::::::::::::::::::::::::

## Figures

You can also include figures:

```{r pyramid}
pie(
  c(Sky = 78, "Sunny side of pyramid" = 17, "Shady side of pyramid" = 5), 
  init.angle = 315, 
  col = c("deepskyblue", "yellow", "yellow3"), 
  border = FALSE
)
```


## Math

One of our episodes contains $\LaTeX$ equations when describing how to create
dynamic reports with {knitr}, so we now use mathjax to describe this:

`$\alpha = \dfrac{1}{(1 - \beta)^2}$` becomes: $\alpha = \dfrac{1}{(1 - \beta)^2}$

Cool, right?

::::::::::::::::::::::::::::::::::::: keypoints 

- Use `.Rmd` files for lessons even if you don't need to generate any code
- Run `sandpaper::check_lesson()` to identify any issues with your lesson
- Run `sandpaper::build_lesson()` to preview your lesson locally

::::::::::::::::::::::::::::::::::::::::::::::::

<!-- Please do not delete anything below this line -->

```{r links, child = sandpaper::template_links()}
```
